Code used to generate paper results : Database comparison and CT characteristics

### 2023-11-17 Paper_code-Database_CT.Rmd

```{r upste_clusters}
upset(fromList(list(LUSC = LUSC_cluster3,
               LUAD1 = LUAD_cluster3,
               LUAD2 = LUAD_cluster4,
               BRCA1 = BRCA_cluster1,
               BRCA2 = BRCA_cluster2)))
```

There is quite a lot of similarities here between the clusters.

>>>>

```{r upset_clusters}
upset(fromList(list(LUSC = LUSC_cluster3,
               LUAD1 = LUAD_cluster3,
               LUAD2 = LUAD_cluster4,
               BRCA1 = BRCA_cluster1,
               BRCA2 = BRCA_cluster2)))
```

There is quite a lot of similarities here between the clusters. Let's look at
the expression in tumours.

```{r TCGA_clusters}
TCGA_expression(c(LUSC_cluster3, LUAD_cluster3, LUAD_cluster4, BRCA_cluster1,
                  BRCA_cluster2),
                tumor = "all", units = "log_TPM")
```
